---
output: html_document
---

# Load essential packages
```{r}
# remotes::install_github("rstudio/distill")
# remotes::install_github("rstudio/rmarkdown")
```

```{r}
if (!require(xfun)) install.packages("xfun")
pkgs <- c(
  "distill",
  "postcards",
  "devtools",
  "usethis",
  "roxygen2",
  "sinew",
  "rmarkdown",
  "here",
  "fs"
)

xfun::pkg_attach2(pkgs, message = FALSE)
```

# Create a website / blog
website is a collection of pages while blog is a collection of posts.  

**Note on distill blog**:
- it is a website with blog posts.  
- it has a special page called listing page.  
- it requires to render each post to work.

```{r}
meta <- list(
  dir = "blog2",
  blog_title <- "Piyayut's Blog",
  author <- "Piyayut Chitchumnong",
  gh <- "https://github.com/piyayut-ch"
)

create_website(dir = meta$dir, title = meta$title, , gh_pages = TRUE)
# create_blog(dir = meta$dir, title = meta$title)
# setwd(meta$dir)
```

```{r}
setwd(meta$dir)
```

```{r}
create_postcard(file = "tobi.Rmd")
```

```{r}
create_article(file = "tobi",         # future name of .Rmd file
               template = "jolla",    # name of template
               package = "postcards") # package that includes the template
```

```{r}
create_theme("postcards")
```

```{r}

```

```{r}

```

## Config `_site.yml`

```{r eval=FALSE}
---
name: ""
title: ""
description: |
  <some text>
base_url: <url>
navbar:
  logo: <path to png>
  search: false/true
  right:
    - text: "Home"
      href: index.html
    - text: "About"
      href: about.html
    - icon: fa fa-facebook
      href: <url>
    - icon: fa fa-github
      href: <url>
    - icon: fa fa-twitter
      href: <url>
    - icon: fa fa-rss
      href: index.xml
  source_url: <url>
google_analytics: ""
twitter:
  site: "@user"
  creator: "@user"
collections:
  posts:
    feed_item_max: num or false
    disqus: <disqus shortname>
rss:
  full_content: true/false
  categories:
    - 
output: distill::distill_article
---
```

# about.Rmd

```{r}
create_postcard(file = "about.Rmd")
```

# gallery.Rmd


# index.Rmd


# Create a post / article

```{r}
distill::create_article("")
distill::create_post("setup-R", draft = TRUE)
```

```{r}
distill::create_theme("theme_distill.css")
```

## config post yml

```{r eval=FALSE}
---
title: ""
description: |
  "some text"
date: "yyyy-mm-dd" or Sys.Date()
author:
  - first_name: "Piyayut"
    last_name: "Chitchumnong"
    url: https://github.com/piyayut-ch
    affiliation: NABC
    affiliation_url: https://www.nabc.org
    orcid_id: 0000-0003-0645-5666
categories:
  - 
bibliography: biblio.bib
citation: true/false
preview: <path>
output:
  distill::distill_article:
    toc: true
    toc_depth: 2
    self_contained: false
draft :true/false
---
```

## render blog

```{r}
blog_date <- "2021-02-25"
blog_title <- "setup-r"
rmarkdown::render(glue::glue("_posts/{blog_date}-{blog_title}/{blog_title}.Rmd"))
```

## render website

```{r}
rmarkdown::render_site()
```

# Publish via Github Page

```{r}
file.create(".nojekyll")
```
